# 参考但不纳入文本的表格、图示和图表

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F,warning = F, message = F)
output_format <- knitr::opts_knit$get("rmarkdown.pandoc.to")
source(paste0(Sys.getenv("USERPROFILE"),"/OneDrive/Work Yeedo/Other/Code/table_format.R"), local = knitr::knit_global())
```
```{r}
source("../Code/book_script.R", local = knitr::knit_global())
```
```{r}
source("../Code/shell-table-function.R", local = knitr::knit_global())
```
```{r}
column = c("试验组", "对照组", "合计")
```


:::{custom-style="SHELL-14-01-节标题2"}
人口学及基线资料
:::
```{r}
formoid <- "入组受试者分布"
population <- "筛选集"
word_style <- "SHELL-14-01-表"
title <- add_title(formoid, population, word_style)

```

`r title`

```{r}
formoid <- "受试者筛选情况汇总"
population <- "筛选集"
word_style <- 'SHELL-14-01-表续'
title <- add_title(formoid, population, word_style)

```
`r title`


```{r}
formoid = "DM"
population = "筛选集"
title <- add_title(formoid, population, "SHELL-14-01-表")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("label" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid = "MH2"
population = "筛选集"
title <- add_title(formoid, population, "SHELL-14-01-表")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`



```{r}
formoid = "QRS2"
population <- "全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid = "TU1"
population <- "全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid = "LB10"
population <- "全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB16"
population <- "全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

:::{custom-style="SHELL-14-01-节标题2"}
疗效和其他非安全性数据
:::

:::{custom-style="SHELL-14-01-节标题2"}
安全性数据
:::

```{r}
formoid <- "CM1"
population <- "全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "PR1"
population <- "全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB1"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB3"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB4"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB5"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB6"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB7"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB8"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB9"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB10"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB11"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB12"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB13"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB14"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "LB15"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`


```{r}
formoid <- "LB16"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "PE"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "QRS1"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "TU2"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "TU3"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "VS1"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`

```{r}
formoid <- "VS2"
population <- "安全数据集"
title <- add_title(formoid, population, "SHELL-14-01-表续")
mock_shell <- make_mock_shell_table(formoid = formoid, 
                                    column= column, 
                                    footnote_vec = c()
                                    )
table <- mock_shell$table%>%set_header_labels("group" = "")
footnote <- mock_shell$footnote
```

`r title`
`r table`
`r footnote`




\newpage